Fusion Moves for Correlation Clustering

### 2014-11-10 paper/anytimefigure2.tex

%!TEX root = egpaper_for_review.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[  mark size=1pt,
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}\label{fig:at:image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \anytimeplot{knott-3d-150}
    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/knott-3d-150.data};

@@

  legend columns=6

@@

  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/socialnets.data};              \addlegendentry{HC}
  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/socialnets.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/socialnets.data};               \addlegendentry{CGC}
  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/socialnets.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/socialnets.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/socialnets.data};    \addlegendentry{Fusion-HC-CGC}
  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/socialnets.data};  \addlegendentry{Fusion-WS-CGC}
  %\anytimeplot{socialnets} 

@@

  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/normalizedsocialnets.data};              \addlegendentry{HC}
  %\addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/normalizedsocialnets.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/normalizedsocialnets.data};               \addlegendentry{CGC}
  %\addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/normalizedsocialnets.data};          \addlegendentry{KL}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/normalizedsocialnets.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/normalizedsocialnets.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/normalizedsocialnets.data};    \addlegendentry{Fusion-HC-CGC}
  %\addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/normalizedsocialnets.data};  \addlegendentry{Fusion-WS-CGC}
 % \anytimeplot{normalizedsocialnets}

@@

@@

@@

    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/modularity-clustering.data};

>>>>

%!TEX root = egpaper_for_review.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[  mark size=1pt,
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]
  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/image-seg.data};    \addlegendentry{PIVOT-BOEM}  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}

  \caption{image-seg}\label{fig:at:image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/knott-3d-150.data};          \addlegendentry{PIVOT-BOEM}
    \anytimeplot{knott-3d-150}

@@

  %legend to name = ledgendPosition,
  legend columns=6,

@@

  \anytimeplot{socialnets} 

@@

  \anytimeplot{normalizedsocialnets}

@@

  legend columns=6,
  scaled ticks = false%,
  %every axis legend/.code={\let\addlegendentry\relax} 

@@

  \addplot[color=yellow,mark=o] table[x=time, y=PIVOT*]{data3/modularity-clustering.data};    \addlegendentry{PIVOT-BOEM} 

@@
